### 2017-10-22 examples/flights_examples.Rmd
Update pkgdown

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(tidyverse)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = params$num_rows) %>% 
  mutate(half_year = case_when(
    between(month, 1, 6) ~ "h1",
    between(month, 7, 12) ~ "h2"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, half_year, 
         day_hour, origin, carrier)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = params$num_rows) %>% 
  mutate(half_year = case_when(
    between(month, 1, 6) ~ "h1",
    between(month, 7, 12) ~ "h2"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, half_year, 
         day_hour, origin, carrier)
```
